---
title: "CSR with sf"
author: "Caitlin Sarro"
date: "10/21/2021"
output: 
  xaringan::moon_reader:
    css: [default, 'simons-touch.css', metropolis, metropolis-fonts] 
    yolo: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# xaringan::inf_mr()
```



# Importing the relevant libraries 
```{r}
# install.packages("pagedown")
# install.packages("xaringan")
library(pagedown)
library(xaringan)

# install.packages("xaringanBuilder")
# install.packages("chromote")
library(xaringanBuilder)
library(chromote)


```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Print the Slides

```{r pressure}

```


